\documentclass[10pt]{article}
\usepackage[margin=0.55in]{geometry}
\usepackage[most]{tcolorbox}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{array}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage[T1]{fontenc}
\usepackage{titlesec}
\usepackage{listings}
\usepackage{tikz}
\usepackage{graphicx}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric}

\definecolor{tmblue}{HTML}{0F172A}
\definecolor{tmgray}{HTML}{475569}
\definecolor{tmaccent}{HTML}{1D4ED8}
\definecolor{tmgreen}{HTML}{166534}
\definecolor{tmred}{HTML}{991B1B}
\definecolor{vscodebg}{HTML}{1E1E1E}

\lstset{
    language=C++,
    basicstyle=\ttfamily\scriptsize\color{white},
    keywordstyle=\color{blue!40},
    stringstyle=\color{orange},
    commentstyle=\color{green!40},
    backgroundcolor=\color{vscodebg},
    frame=single,
    rulecolor=\color{tmgray},
    breaklines=true,
    showstringspaces=false,
    aboveskip=15pt,
    belowskip=15pt
}

\titleformat{\section}{\large\bfseries\color{tmblue}}{\thesection}{0.5em}{}
\titleformat{\subsection}{\normalsize\bfseries\color{tmblue}}{\thesubsection}{0.5em}{}
\titleformat{\subsubsection}{\normalsize\bfseries\color{tmgray}}{\thesubsubsection}{0.5em}{}

\setlength{\parindent}{0pt}
\setlength{\parskip}{5pt}

\begin{document}

\begin{center}
    {\huge \bfseries \color{tmblue} Liquidity Intelligence Console Implementation Report}\\[10pt]
    {\large \color{tmgray} Real-Time Multi-Asset Exchange Benchmarking Dashboard}\\[5pt]
    \rule{\textwidth}{1pt}
\end{center}

\vspace{10pt}

\section{Project Overview}
The Liquidity Intelligence Console is a real-time observability platform designed to benchmark True Markets' liquidity against other exchanges (Kraken, Crypto.com) on the BTC-PYUSD trading pair. The system monitors orderbook depth, spread variance, and execution latency across venues using a threaded C++ data engine and a React/Vite visualization dashboard.

\section{System Architecture \& Technical Achievement}
The implementation is vertically integrated across two core layers:
\begin{itemize}[leftmargin=*]
    \item \textbf{C++ Market Data Engine:} Built with \texttt{uWebSockets} and \texttt{libcurl}. The engine polls Kraken and Crypto.com REST APIs for BTC-PYUSD orderbook data, computes spread/depth metrics, and broadcasts JSON payloads to the frontend via WebSocket.
    \item \textbf{True Markets CeFi Direct WebSocket:} The frontend connects directly to the True Markets CeFi WebSocket (\texttt{wss://uat.truex.co/api/v1}) using unauthenticated DEPTH and EBBO channel subscriptions for real-time orderbook data.
    \item \textbf{React Visualization Dashboard:} Built on Vite with React and Tailwind v4. Renders side-by-side orderbooks, dislocation history charts, microprice calculations, and a time-aware insight engine.
\end{itemize}

\subsection{Multi-Venue Data Routing}
The frontend dictates the active benchmark venue via WebSocket messages to the C++ backend. Since all venues now use the same BTC-PYUSD pair, no volume normalization is needed --- the comparison is direct and honest.

\begin{lstlisting}[caption=Dynamic Exchange Interpolation in C++]
auto fetch_benchmark = [&](const std::string& asset, const std::string& bench) -> VenueSnapshot {
    std::string url;
    if (bench == "Binance") {
        std::string symbol = asset + "USDT";
        url = "https://api.binance.us/api/v3/depth?symbol=" + symbol + "&limit=5";
        return fetch_binance_snapshot(url);
    } else {
        std::string symbol = asset + "-USD";
        url = "https://api.exchange.coinbase.com/products/" + symbol + "/book?level=2";
        VenueSnapshot raw = fetch_coinbase_snapshot(url);
        scale_coinbase_volumes(raw); // Normalization pass
        return raw;
    }
};
\end{lstlisting}

\section{Liquidity Insight Engine (Frontend Intelligence)}
The most recent structural addition is the automated Liquidity Insight Engine. By directly processing incoming depth matrices natively in React, the system acts as an algorithmic observer, flagging underlying issues regarding Spread Yields, Mid-Price Arbitrage Gaps, and Orderbook Momentum Imbalance natively mapping metrics from the C++ raw output state.

\begin{lstlisting}[caption=React Inference Computing Microprice]
// Computing Microprice (volume-weighted mid price) recursively from top-tier depths
let microprice = snapshot.mid;
if (snapshot.bids.length > 0 && snapshot.asks.length > 0) {
    const topBidP = snapshot.bids[0][0]; const topBidQ = snapshot.bids[0][1];
    const topAskP = snapshot.asks[0][0]; const topAskQ = snapshot.asks[0][1];
    microprice = (topBidP * topAskQ + topAskP * topBidQ) / (topBidQ + topAskQ);
}
\end{lstlisting}

\section{Presentation UI \& Terminal Constraints}
In the Vite interface, aesthetics were optimized strictly toward a HFT trading interface. Constraints applied:
\begin{itemize}
    \item \textbf{True \texttt{100vw} Padding Bound}: Stripped standard \texttt{w-screen} metrics to map limits using \texttt{max-w-[1600px] lg:p-10} preventing numeric bleeding outside wide-monitor limits.
    \item \textbf{Diagnostic Layout}: Split standard vertically cascading divs into a strictly locked Left (60\% Spread Charts) and Right (40\% Fixed Side-by-Side Orderbooks) container logic utilizing dense \texttt{0.2em} tracking on sub-headers.
\end{itemize}

\vspace{10pt}

\begin{tcolorbox}[colback=tmblue!5, colframe=tmblue, title=Live Console Demo]
    \centering
    \textit{Run \texttt{./run\_demo.sh} and open \texttt{http://localhost:5173} for the live dashboard.}
\end{tcolorbox}

\section{True Markets API Integration}
The dashboard connects directly to the True Markets CeFi Direct WebSocket at \texttt{wss://uat.truex.co/api/v1} using unauthenticated subscriptions (\texttt{SUBSCRIBE\_NO\_AUTH}). It subscribes to the \texttt{DEPTH} and \texttt{EBBO} channels for the \texttt{BTC-PYUSD} instrument, receiving real-time orderbook snapshots. If the True Markets WebSocket is unavailable, the system automatically falls back to a simulated feed derived from the benchmark venue data.

\section{Conclusion}
The platform provides real-time multi-venue liquidity comparison with honest metric sourcing and a clean component architecture designed for extensibility.

\end{document}
